MS Depression Paper, post replication, started 2022 09 21

### 2023-07-21 scripts/msdepression_n380_started_20230113_post_replication_just_simple_mm.Rmd
with age

#with age; diagnosis: Dep > nondep T = 2.4, p = 0.015; Network dep>nondep = T=12.4, p = 2*10^-16; intx = T = 2.3, p = 0.020
diagnosis_by_network_interaction_lmer_age <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject) + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
summary(diagnosis_by_network_interaction_lmer_age)

#Diagnosis: MS+ > MS- 0.011-0.1; Network dep>nondep -.104--.076; intx: -0.040--0.003
confint(diagnosis_by_network_interaction_lmer_age)

>>>>

#with age; diagnosis: Dep > nondep T = 2.1, p = 0.035; Network dep>nondep = T=12.4, p = 2*10^-16; intx = T = 2.3, p = 0.020
diagnosis_by_network_interaction_lmer_age <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject) + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
summary(diagnosis_by_network_interaction_lmer_age)

#Diagnosis: MS+ > MS- 0.004-0.9; Network dep>nondep -.104--.076; intx: -0.040--0.003
confint(diagnosis_by_network_interaction_lmer_age)
